---
title: "How to compute the exponential of a number using the truncated series expansion"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to compute the exponential of a number using the truncated series expansion}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Project3He)
```


The exponential of a number can be written as an infinite series expansion of the form
$$
\exp(x) = 1 + x + \frac{x^2}{2!} + \frac{x^3}{3!} + \cdots
$$


The truncated sum of terms means the sum of terms that excludes values exceeding a certain threshold value, which represents an approximation to the true exponential. The `Exp(x,k)` function computes the exponential of a number using the truncated series expansion.


An example of the `Exp(x,k)` function:


```{r}
Exp(2, 5)
```


For a given value $x$, as $k$ increases, the value of `Exp(x,k)` function will approximate the value of `exp(x)` from base R.


A way to show this approximation is to apply different values of $k$ to a given value of $x$.


```{r}
# Taylor series approximation
# Set x = 5
Exp(5,k=1)
Exp(5,k=5)
Exp(5,k=10)
Exp(5,k=100)
```


```{r}
# compared to 
exp(5)
```


Another way to show this approximation is to visualize the value of the two functions for a given value of $x$ with different values of $k$.


```{r, message = FALSE}
require(tidyverse)
```


```{r}
tibble(x = rep(5, 100)) %>%
    mutate(k = seq(1, 100, by = 1)) %>%
    mutate(Exp = sapply(1:100, function(x) Exp(5, x))) %>%
    ggplot(aes(x = k, y = Exp)) +
    geom_point(size = 2) +
    geom_line(size = 1) +
    geom_hline(yintercept = exp(5)) +
    theme_bw()
```


As shown in the figure above, as $k$ increases, the value of $Exp(5, k)$ approximates to the value of $exp(5)$.
